---
title: "ReconTime"
output: html_document
date: "2023-04-05"
---

#clear

```{r}
# clear workspace
rm(list = ls())
```

# Housekeeping

```{r}
wd = 'C:/Users/micha.engeser/Documents/GitHub/Reconstructed_time_analysis'
setwd(wd)
dir()
if (!('tidyverse' %in% installed.packages()))
{install.packages("tidyverse")}
library(tidyverse)

if (!('dplyr' %in% installed.packages()))
{install.packages('dplyr')}
library(dplyr)

if (!('ggdist' %in% installed.packages()))
{install.packages('ggdist')}
library(ggdist)

if (!('brms' %in% installed.packages()))
{install.packages('brms')}
library(brms)

if (!('lme4' %in% installed.packages()))
{install.packages('lme4')}
library(lme4)

if (!('lmerTest' %in% installed.packages()))
{install.packages('lmerTest')}
library(lmerTest)

if (!('optimx' %in% installed.packages()))
{install.packages('optimx')}
library(optimx)

if (!('car' %in% installed.packages()))
{install.packages('car', dependencies = TRUE)}
library(car)


```

# details of subjects  

```{r}
subNums = c(101, 102, 103, 105, 106, 107, 108, 109, 110, 111)
ses = 1
Lab_ID = 'SX'
task = 'prp'
```

# loading files

```{r}
count = 0
sub_ids = NaN
for (subNum in subNums ){
count = count + 1
sub_ids[count] = paste0(Lab_ID, subNum)

sub_folder = paste0('sub-', Lab_ID, subNum)
ses_folder = paste0('ses-', ses)
file_name = paste0(sub_folder, '_', ses_folder, '_run-all_task-', task,'_events.csv')

setwd("..")
parent_dir = getwd()
setwd(wd)
file = file.path(parent_dir, 'Reconstructed_time_experiment', 'data', sub_folder, ses_folder, file_name)
event_table = read.csv(file)

# make format consistent
if ('X' %in% colnames(event_table))
{event_table$X <- NULL}

colnames(event_table)[which(names(event_table) == "has_repsonse_vis")] <- "has_response_vis"
colnames(event_table)[which(names(event_table) == "trial_repsonse_vis")] <- "trial_response_vis"

# add subject number column 
event_table = event_table %>% mutate(sub_num = subNum)

# concatanate the tables
if ( exists('all_event_table')){
  all_event_table = rbind(all_event_table, event_table)
} else {
  all_event_table = event_table
}
}
```

# make downsampling for introspective task 

```{r}

all_event_table = all_event_table %>% filter(SOA != 0.116)

all_event_table = all_event_table[sample(1:nrow(all_event_table)), ]


task_relevance_lvl = c('non-target', 'irrelevant')
SOA_lock_lvl = c('onset', 'offset')
SOA_lvl = c(0,0.232,0.466)
duration_lvl = c(0.5,1,1.5)
sub_id_lvl = sub_ids


for (o in sub_id_lvl){
  for (i in SOA_lvl){
    for (ii in SOA_lock_lvl) {
      for (iii in task_relevance_lvl) {
        for (iv in duration_lvl) {
          
          cell_trials = sum(all_event_table$sub_id == o & all_event_table$SOA == i & all_event_table$SOA_lock == ii & all_event_table$task_relevance == iii & all_event_table$duration == iv, na.rm = TRUE)
          
          cell_table = all_event_table %>% filter(sub_id == o & SOA == i & SOA_lock == ii & task_relevance == iii & duration == iv)
          
          cell_table = cell_table[1:round(40/3), ]
          
          if (exists("new_event_table")){
new_event_table = rbind(new_event_table, cell_table)
          } else {
            new_event_table = cell_table
          }
         
        }}}}}

# check if downsampling was successful 
for (o in sub_id_lvl){
  for (i in SOA_lvl){
    for (ii in SOA_lock_lvl) {
      for (iii in task_relevance_lvl) {
          
          cell_trials = sum(new_event_table$sub_id == o & new_event_table$SOA == i & new_event_table$SOA_lock == ii & new_event_table$task_relevance == iii, na.rm = TRUE)
          

          if(cell_trials != 39){
            cell_name = paste(i,ii,iii,iv,sep= '-')
            warning(paste0('Subject ',o,' has ', cell_trials,' trials for cell: ', cell_name, '\n'))
          }
      }}}}

all_event_table = new_event_table

```

# apply trial exclusion

```{r}
# without exclusion
raw_event_table = all_event_table

# remove target trials 
all_event_table = all_event_table[all_event_table$task_relevance != 'target', ]
relevant_event_table = all_event_table[all_event_table$task_relevance == 'non-target', ]
irrelevant_event_table = all_event_table[all_event_table$task_relevance == 'irrelevant', ]

# remove false alarm 
all_event_table = all_event_table[all_event_table$trial_response_vis != 'fa', ]

# remove RT < 100 ms
all_event_table = all_event_table[all_event_table$RT_aud > 0.1, ]

# remove incorrect auditory responses
all_event_table = all_event_table[all_event_table$trial_accuracy_aud == 1, ]

# remove outliers

# sample_mean = mean(all_event_table$RT_aud, na.rm = TRUE)
# sample_sd = sd(all_event_table$RT_aud, na.rm = TRUE)
# remove RT > 3x std
# all_event_table = all_event_table[all_event_table$RT_aud < sample_mean + 4*sample_sd, ]

# remove RT < 3x std
# all_event_table = all_event_table[all_event_table$RT_aud > sample_mean - 4*sample_sd, ]

# remove NaNs from auditory responses
all_event_table = all_event_table[!is.na(all_event_table$trial_accuracy_aud), ]


# sum(is.na(all_event_table$trial_accuracy_aud[all_event_table$SOA_lock == 'offset']), na.rm = TRUE)
# sum(is.na(all_event_table$trial_accuracy_aud[all_event_table$SOA_lock == 'onset']), na.rm = TRUE)

# check if any combination of condition (cell) has less than 30 trials 

task_relevance_lvl = c('non-target', 'irrelevant')
SOA_lock_lvl = c('onset', 'offset')
SOA_lvl = c(0,0.116,0.232,0.466)
duration_lvl = c(0.5,1,1.5)
sub_id_lvl = sub_ids


for (o in sub_id_lvl){
  for (i in SOA_lvl){
    for (ii in SOA_lock_lvl) {
      for (iii in task_relevance_lvl) {
        for (iv in duration_lvl) {
          
          cell_trials = sum(all_event_table$sub_id == o & all_event_table$SOA == i & all_event_table$SOA_lock == ii & all_event_table$task_relevance == iii & all_event_table$duration == iv, na.rm = TRUE)
          

          if(cell_trials < 30){
            cell_name = paste(i,ii,iii,iv,sep= '-')
            warning(paste0('Subject ',o,' has only ', cell_trials,' trials for cell: ', cell_name, '\n'))
          }
        }}}}}

```

# process data 

```{r}

# take mean for each participant

all_data = all_event_table %>%  group_by(sub_id, SOA, SOA_lock, task_relevance, duration) %>% summarise(mean_RT = mean(RT_aud, na.rm = TRUE), sd_RT = sd(RT_aud, na.rm = TRUE))

SOA_SOA_lock_data = all_event_table %>%  group_by(SOA, SOA_lock) %>%
                                      summarise(mean_RT = mean(RT_aud, na.rm = TRUE),
                                                         sd_RT = mean(RT_aud, na.rm = TRUE))

SOA_SOA_lock_task_relevance_data = all_event_table%>%  group_by(SOA, SOA_lock, task_relevance) %>%
                                      summarise(mean_RT = mean(RT_aud, na.rm = TRUE),
                                                         sd_RT = mean(RT_aud, na.rm = TRUE))

SOA_SOA_lock_duration_data = all_event_table %>%  group_by(SOA, SOA_lock, duration) %>%
                                      summarise(mean_RT = mean(RT_aud, na.rm = TRUE),
                                                         sd_RT = mean(RT_aud, na.rm = TRUE))
```

## TRANSFORM DATA

``` {r}
# add log transformed column
all_event_table = all_event_table %>% mutate(log_RT_aud = log(RT_aud))

# add response window column 
all_event_table = all_event_table %>% mutate(resp_window = (2-onset_SOA)+stim_jit )

# make task relevance and SOA lock numeric
all_event_table = all_event_table %>% mutate(is_task_relevant = ifelse(task_relevance == 'non-target',1,0)) 
all_event_table = all_event_table %>% mutate(is_onset = ifelse(SOA_lock == 'onset',1,0))
all_event_table = all_event_table %>% mutate(ori_num = unclass(as.factor(orientation))) # 1=center, 2=left, 3=right 
all_event_table = all_event_table %>% mutate(cate_num = unclass(as.factor(category))) # 1=face, 2=false_font, 3=letter, 4=object

# center variables 
all_event_table = all_event_table %>% mutate(c_task_relevant = is_task_relevant - mean(is_task_relevant))
all_event_table = all_event_table %>% mutate(c_is_onset = is_onset - mean(is_onset))
all_event_table = all_event_table %>% mutate(c_SOA = SOA - mean(SOA))
all_event_table = all_event_table %>% mutate(c_duration = duration - mean(duration))
all_event_table = all_event_table %>% mutate(c_pitch = (pitch-1050)/100) # makes pitches 0.5 for high and -0.5 for low
all_event_table = all_event_table %>% mutate(c_cate_num = cate_num - mean(cate_num)) # center cate num

```
# plotting

```{R}
# make duration a string
event_table2 = all_event_table
event_table2$duration = as.character(event_table2$duration)

# histograms

#all
hist_1 = ggplot(event_table2, aes(x=RT_aud)) + 
  geom_histogram(bins = 30) + xlim(c(0,2))
hist_1
# split by duration
hist_2 = ggplot(event_table2, aes(x=RT_aud, fill=duration)) +
  geom_histogram(alpha=0.6, position='identity') + xlim(c(0,2))
hist_2
# split by task relevance
hist_3 = ggplot(event_table2, aes(x=RT_aud, fill=task_relevance)) +
  geom_histogram(alpha=0.6, position='identity') + xlim(c(0,2))
hist_3
# split by SOA-lock
hist_4 = ggplot(event_table2, aes(x=RT_aud, fill=SOA_lock)) +
  geom_histogram(alpha=0.6, position='identity') + xlim(c(0,2))
hist_4


# line plots 

p1 = ggplot(data=SOA_SOA_lock_data, aes(x=SOA*1000, y=mean_RT*1000, group=SOA_lock)) +
  geom_line(aes(linetype = SOA_lock))+
  geom_point()+
  ylim(c(400,700))+
  ylab("Reaction time [ms]")+
  xlab('SOA [ms]')
p1

p2 = ggplot(data=SOA_SOA_lock_duration_data, aes(x=SOA*1000, y=mean_RT*1000, group=interaction(as.character(duration), SOA_lock))) +
  geom_line(aes(color=as.character(duration), linetype = SOA_lock))+
  geom_point()+
  ylim(c(400,700))+
  ylab("Reaction time [ms]")+
  xlab('SOA [ms]')+
  scale_color_manual(values=c('red','blue','green'))
p2

p3 = ggplot(data=SOA_SOA_lock_task_relevance_data, aes(x=SOA*1000, y=mean_RT*1000, group=interaction(task_relevance, SOA_lock))) +
  geom_line(aes(color=task_relevance, linetype = SOA_lock))+
  geom_point()+
  ylim(c(400,700))+
  ylab("Reaction time [ms]")+
  xlab('SOA [ms]')+
  scale_color_manual(values=c('red','blue'))
p3



```

# rain cloud plot

```{r}

source("R_rainclouds.R")


# prepare data 
n = length(subNums)

rp_data = all_event_table %>%  group_by(SOA, SOA_lock, sub_id) %>%
                                      summarise(mean_RT = mean(RT_aud, na.rm = TRUE),
                                                         sd_RT = sd(RT_aud, na.rm = TRUE))

sum_data = rp_data %>%  group_by(SOA, SOA_lock) %>%
                                      summarise(RT_mean = mean(mean_RT, na.rm = TRUE),
                                                         RT_median = median(mean_RT, na.rm = TRUE),
                                                         RT_sd = sd(mean_RT, na.rm = TRUE),
                                                         RT_sem = RT_sd / sqrt(n))

rp_data$SOAj = jitter(rp_data$SOA, amount = .005)


# define colors
fill_colors = c(rep("pink",5),rep("lightblue",5))
line_colors = c("onset" = "blue", "offset" = "red")

#Rainclouds for repeated measures, additional plotting options 

ggplot(rp_data, aes(x = SOA, y = mean_RT, fill = SOA_lock)) +
  # distribution plot
  geom_flat_violin(aes(fill = interaction(SOA_lock,SOA)),position = position_nudge(x = .02, y = 0), adjust = 1.5, trim = FALSE, alpha = .5, colour = NA)+ 
  # connecting individual data points (onset-locked)
  geom_line(data = rp_data %>% filter(SOA_lock =="onset"), aes(x=SOAj+.02, y = mean_RT, group=sub_id), color = 'lightblue',linetype = 1, size=0.1)+
  # connecting individual data points (offset-locked)
  geom_line(data = rp_data %>% filter(SOA_lock =="offset"), aes(x=SOAj+.02, y = mean_RT, group=sub_id), color = 'pink',linetype = 1, linewidth=0.1)+ 
  # individual data points (each subject)
  geom_point(aes(x = as.numeric(SOAj)+.02, y = mean_RT, colour = SOA_lock), size = 0.5, shape = 20) +
  # box plots
  geom_boxplot(aes(x = SOA, y = mean_RT, fill = interaction(SOA_lock,SOA)),outlier.shape = NA, alpha = .5, width = .02, colour = "black")+
  # error bars
  geom_errorbar(data = sum_data, aes(x = as.numeric(SOA)+.02, y = RT_mean, group = SOA_lock, colour = SOA_lock, ymin = RT_mean-RT_sem, ymax = RT_mean+RT_sem), width = .005)+ 
  # mean line
  geom_line(data = sum_data, aes(x = as.numeric(SOA)+.02, y = RT_mean, group = SOA_lock, colour = SOA_lock),linetype = 2, size=0.5)+
  # mean points
  geom_point(data = sum_data, aes(x = as.numeric(SOA)+.02, y = RT_mean, group = SOA_lock, colour = SOA_lock), shape = 18, size=1)+
  # adjust colors 
  scale_fill_manual(values=fill_colors )+scale_color_manual(values = line_colors)

ggsave('../figures/raincloud.png', width = 6, height = 4)


```

# box plot 

```{r}


# box plots 
box_plot_data = data.frame(matrix(ncol = 0, nrow = 0))
counter2 = 0
col_names = "nan"

  for (i in SOA_lock_lvl){
    for (ii in SOA_lvl) {
      for (iii in task_relevance_lvl) {
        for (iv in duration_lvl) {
                    
          counter2 = counter2 + 1 
          col_names[counter2] = paste(i,ii,iii,iv,sep = "_")
          for (o in 1:length(subNums)){

          box_plot_data[o,counter2] = mean(all_event_table$RT_aud[all_event_table$sub_id == sub_id_lvl[o] & all_event_table$SOA_lock == i & all_event_table$SOA == ii & all_event_table$task_relevance == iii & all_event_table$duration == iv], na.rm = TRUE)
}}}}}


colors = c(rep("red",3),rep("darkred",3),rep("green",3),rep("darkgreen",3),rep("blue",3),rep("darkblue",3),rep("yellow",3), rep("orange",3))

ggplot(all_data, aes(SOA_lock, mean_RT, fill=interaction(duration, task_relevance, SOA))) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() +
  scale_fill_manual(values=colors)

```

# main analysis

```{r}

# full general linear mixed effect model

full_model = glmer(RT_aud ~ c_SOA*is_onset*c_duration*is_task_relevant + (1*c_SOA*is_onset*c_duration*is_task_relevant|sub_num), family=Gamma(link="identity"), data=all_event_table)
summary(full_model)
Anova(full_model)
plot(fitted(full_model),residuals(full_model))
qqnorm(residuals(full_model))

# reduced general linear mixed effect model (without duration, if duration is not significant in the full model)

reduced_model = glmer(RT_aud ~ c_SOA*is_onset*is_task_relevant + (1*c_SOA*is_onset*is_task_relevant|sub_num), family=Gamma(link="identity"), data=all_event_table)
summary(reduced_model)
Anova(reduced_model)
plot(fitted(reduced_model),residuals(reduced_model))
qqnorm(residuals(reduced_model))

```


# exploratory split by SOA-lock analayses - models

```{r}
# offset general linear mixed effect model

offset_event_table = all_event_table %>% filter(SOA_lock == 'offset')


offset_model = glmer(RT_aud ~ c_SOA*c_duration*is_task_relevant + (1*c_SOA*c_duration*is_task_relevant|sub_num), family=Gamma(link="identity"), data=offset_event_table)
summary(offset_model)
Anova(offset_model)
plot(fitted(offset_model ),residuals(offset_model))
qqnorm(residuals(offset_model))


# onset general linear mixed effect model

onset_event_table = all_event_table %>% filter(SOA_lock == 'onset')


onset_model = glmer(RT_aud ~ c_SOA*c_duration*is_task_relevant + (1*c_SOA*c_duration*is_task_relevant|sub_num), family=Gamma(link="identity"), data=onset_event_table)
summary(onset_model)
Anova(onset_model)
plot(fitted(onset_model ),residuals(onset_model))
qqnorm(residuals(onset_model))


```

# exploratory control analayses - plots

```{r}

# pitch  

SOA_SOA_lock_pitch_data = all_event_table %>%  group_by(SOA, SOA_lock, c_pitch) %>%
                                      summarise(mean_RT = mean(RT_aud, na.rm = TRUE),
                                                         sd_RT = mean(RT_aud, na.rm = TRUE))

pitch_plot = ggplot(data=SOA_SOA_lock_pitch_data, aes(x=SOA*1000, y=mean_RT*1000, group=interaction(as.character(c_pitch), SOA_lock))) +
  geom_line(aes(color=as.character(c_pitch), linetype = SOA_lock))+
  geom_point()+
  ylim(c(400,700))+
  ylab("Reaction time [ms]")+
  xlab('SOA [ms]')+
  scale_color_manual(values=c('red','blue','green'))
pitch_plot

# duration with only SOA and no SOA lock 

SOA_duration_data = all_event_table %>%  group_by(SOA, duration) %>%
                                      summarise(mean_RT = mean(RT_aud, na.rm = TRUE),
                                                         sd_RT = mean(RT_aud, na.rm = TRUE))

SOA_duration_id_data = all_event_table %>%  group_by(SOA, duration, sub_id) %>%
                                      summarise(mean_RT = mean(RT_aud, na.rm = TRUE),
                                                         sd_RT = mean(RT_aud, na.rm = TRUE))

SOA_duration_plot = ggplot(data=SOA_duration_data, aes(x=SOA*1000, y=mean_RT*1000, group=as.character(duration))) +
  geom_line(aes(color=as.character(duration)))+
  geom_point()+
  # connecting individual data points (onset-locked)
  geom_line(data = SOA_duration_id_data %>% filter(duration == 0.5), aes(x=SOA*1000, y = mean_RT*1000, group=sub_id), color = 'pink',linetype = 1, size=0.1)+
  # connecting individual data points (onset-locked)
  geom_line(data = SOA_duration_id_data %>% filter(duration == 1), aes(x=SOA*1000, y = mean_RT*1000, group=sub_id), color = 'lightblue',linetype = 1, size=0.1)+
  # connecting individual data points (offset-locked)
  geom_line(data = SOA_duration_id_data %>% filter(duration == 1.5), aes(x=SOA*1000, y = mean_RT*1000, group=sub_id), color = 'lightgreen',linetype = 1, linewidth=0.1)+ 
  # individual data points (each subject)
  geom_point(data = SOA_duration_id_data, aes(x = SOA*1000, y = mean_RT*1000, colour = as.character(duration)), size = 1, shape = 20)+
  ylim(c(400,700))+
  ylab("Reaction time [ms]")+
  xlab('SOA [ms]')+
  scale_color_manual(values=c('red','blue','darkgreen'))
SOA_duration_plot



# category 

SOA_SOA_lock_category_data = all_event_table %>%  group_by(SOA, SOA_lock, category) %>%
                                      summarise(mean_RT = mean(RT_aud, na.rm = TRUE),
                                                         sd_RT = mean(RT_aud, na.rm = TRUE))

category_plot = ggplot(data=SOA_SOA_lock_category_data, aes(x=SOA*1000, y=mean_RT*1000, group=interaction(category, SOA_lock))) +
  geom_line(aes(color=category, linetype = SOA_lock))+
  geom_point()+
  ylim(c(400,700))+
  ylab("Reaction time [ms]")+
  xlab('SOA [ms]')+
  scale_color_manual(values=c('red','blue','green','orange'))
category_plot


# orientation

SOA_SOA_lock_ori_data = all_event_table %>%  group_by(SOA, SOA_lock, orientation) %>%
                                      summarise(mean_RT = mean(RT_aud, na.rm = TRUE),
                                                         sd_RT = mean(RT_aud, na.rm = TRUE))

ori_plot = ggplot(data=SOA_SOA_lock_ori_data, aes(x=SOA*1000, y=mean_RT*1000, group=interaction(orientation, SOA_lock))) +
  geom_line(aes(color=orientation, linetype = SOA_lock))+
  geom_point()+
  ylim(c(400,700))+
  ylab("Reaction time [ms]")+
  xlab('SOA [ms]')+
  scale_color_manual(values=c('red','blue','green'))
ori_plot

# auditory accuracy

acc_data = raw_event_table %>%  group_by(SOA, SOA_lock, task_relevance) %>%
                                      summarise(mean_acc = mean(trial_accuracy_aud, na.rm = TRUE),
                                                         sd_acc = mean(trial_accuracy_aud, na.rm = TRUE))


acc_plot = ggplot(data=acc_data, aes(x=SOA*1000, y=mean_acc*100, group=interaction(SOA_lock, task_relevance)))+
  geom_line(aes(colour = task_relevance, linetype = SOA_lock))+
  geom_point()+
  ylim(c(80,100))+
  ylab("Accuracy in %")+
  xlab('SOA [ms]')
acc_plot
```

# exploratory control analayses - models

```{r}

# pitch  
pitch_model = glmer(RT_aud ~ c_SOA*is_onset*c_duration*is_task_relevant*c_pitch + (1*c_SOA*is_onset*c_duration*is_task_relevant*c_pitch|sub_num), family=Gamma(link="identity"), data=all_event_table)
summary(pitch_model)

# category 
cate_model = glmer(RT_aud ~ c_SOA*is_onset*c_duration*is_task_relevant*cate_num + (1*c_SOA*is_onset*c_duration*is_task_relevant*cate_num|sub_num), family=Gamma(link="identity"), data=all_event_table)
summary(cate_model)

# orientation 
ori_model = glmer(RT_aud ~ c_SOA*is_onset*c_duration*is_task_relevant*ori_num + (1*c_SOA*is_onset*c_duration*is_task_relevant*ori_num|sub_num), family=Gamma(link="identity"), data=all_event_table)
summary(ori_model)

# mega model

mega_model = glmer(RT_aud ~ c_SOA*c_is_onset*c_duration*c_task_relevant + (1*c_SOA*c_is_onset*c_duration*c_task_relevant | sub_num)+ (1*c_SOA*c_is_onset*c_duration*c_task_relevant | c_pitch)+ (1*c_SOA*c_is_onset*c_duration*c_task_relevant | c_cate_num), family=Gamma(link="identity"), data=all_event_table)
summary(mega_model)
Anova(mega_model)



```

# bayesian exploratory analysis - incomplete!

```{r}

library(brms)
install.packages("dampack")
library(dampack)

# data simulation and priors
#gamma_params = gamma_params(mean(all_event_table$RT_aud, na.rm = TRUE), sd(event_table$RT_aud, na.rm = TRUE), scale = FALSE)

#prior1 = rgamma(n=1000,shape=gamma_params$shape,rate=gamma_params$rate)


#brm_SOA_SOA_lock_model = brm(RT_aud ~ c_SOA*is_onset*c_duration*is_task_relevant + (1*c_SOA*is_onset*c_duration*is_task_relevant|sub_num), all_event_table, family=Gamma(link="identity"),save_pars = save_pars(all = TRUE))
#summary(brm_SOA_SOA_lock_model)
#confint(brm_SOA_SOA_lock_model)
#plot(brm_SOA_SOA_lock_model)

#brm_null_model = brm(RT_aud ~ 1, all_event_table, family=Gamma(),save_all_pars = TRUE)
#summary(brm_null_model)
#confint(brm_null_model)


# Calculate the Bayes factor for the model with and without the parameter of interest
#bayes_factor = bayes_factor(brm_SOA_SOA_lock_model, brm_null_model)

#brm_main_mixed_model = brm(RT_aud ~ SOA*SOA_lock*duration*task_relevance + (1+SOA*SOA_lock*duration*task_relevance|sub_id), family = Gamma(), data=all_event_table)
#summary(brm_main_mixed_model)




```

# power analysis

```{r}
if (!('pwr' %in% installed.packages()))
{install.packages("pwr")}
library(pwr)


# from marti paper
f =  47.08
n = 10
df_num = 5
df_denom = 45

# effect size 
eta = (f * df_num ) / (f * df_num  + df_denom )
effect_size = sqrt((df_denom/n)*(eta/(1-eta)))

# Specify  desired power, and significance level
power = 0.80
alpha = 0.05

# degrees of freedom for the numerator for our analysis 
u = 1

# Estimate sample size for GLMM with logistic regression
v = pwr.f2.test(u = u, v = , f2 = effect_size/4, sig.level = .05, power = power)$v

req_sample_size = ceiling(v + u + 1)
  
# (v = n - u - 1\). This implies \(n = v + u + 1\).


```
(Intercept)               0.516229   0.060345   8.555
SOA                      -0.149264   0.021116  -7.069
SOA_lockonset             0.053079   0.027122   1.957
duration                  0.004461   0.006218   0.717
task_relevancenon-target  0.031554   0.016313   1.934
